---
title: "Peer_Assessment_Devasena"
author: "Devasena"
date: "16 August 2014"
output: html_document
---

This Peer Assessment is a part of assignment for Reproducible Research course by Coursera. This assignment makes use of data from a personal activity monitoring device. This device collects data at 5 minute intervals through out the day. The data consists of two months of data from an anonymous individual collected during the months of October and November, 2012 and include the number of steps taken in 5 minute intervals each day.

### Step 1: Loading and preprocessing data

```{r, echo=TRUE}
peer_data = read.csv("activity.csv")
```

### Step 2: Calculating mean total number of steps taken per day (ignoring missing values for this part)

#### 1. Histogram of total number of steps taken each day (Using "group by" clause of SQL in "sqldf")

```{r, echo=TRUE}
library(sqldf)
peer_data_df<-sqldf("select date, sum(steps) SUM_STEP from peer_data group by date")
hist(as.numeric(peer_data_df$SUM_STEP), xlab="Total number of steps per day")
```

#### 2. Calculating and reporting the mean and median of total number of steps taken each day (using same function as above)

##### i) Mean of total number of steps taken each day is as below:

```{r, echo=TRUE}
peer_data_df1<-sqldf("select date, avg(steps) STEP, max(steps) MAX_STEP, min(steps) MIN_STEP from peer_data group by date")

peer_data_df1$STEP
```

##### ii) Median of steps taken each day is as below:

```{r, echo=TRUE}
peer_data_df2<-sqldf("select date, STEP, (MAX_STEP + MIN_STEP)/2 MEDIAN_STEP from peer_data_df1")

peer_data_df2$MEDIAN_STEP
```
